---
title: "Obesity in the USA"
author: "Itamar Simon"
date: "January 3, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## General

- In this presentation I attempted to show obesity rates in the US for each state for years 2012-2016. 
- The original data comes from the following website: <https://chronicdata.cdc.gov/> and the actual data was downloaded from: <https://chronicdata.cdc.gov/api/views/hn4x-zwk7/rows.csv?accessType=DOWNLOAD>
- Due to the fact that the original data source was large, I used a reduced and cleaner version for this app.
- The app could be accessed from the following link: <https://itamarsimon.shinyapps.io/obesity/>


## How it Works

- After opening the app, choose a year, a specific factor of interest (Income, Gender etc.) and a sub factor. 
- **You must choose a value for each filter so that the state will show only one point on the plot.**
- Look in the plot tab to view the rate for each state in the US.
 

## Cleaning the data

```{r cars, echo = FALSE}
# load dataset
library(dplyr)
library(stringr)

url <- "https://chronicdata.cdc.gov/api/views/hn4x-zwk7/rows.csv?accessType=DOWNLOAD"
df <- read.csv(url, header = TRUE) 

# Clean the data
clean <- select(df, c(1, 4, 6, 8, 11, 30, 31)) %>%
  filter(YearStart>2011) %>%
  filter(str_detect(Class, "Obesity / Weight Status")) %>%
  filter(str_detect(Question, "Percent of adults aged 18 years and older who have obesity")) %>%
  select(-3,-4) 
head(clean)
```

## Plot the data example

```{r echo=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
clean <- filter(clean, YearStart == 2012) %>%
  filter(StratificationCategory1 == "Gender") %>%
  filter(Stratification1 == "Male")
g <- ggplot(data = clean, aes(x=LocationDesc, y=Data_Value))+
  geom_point(shape=21)+
  ggtitle("Obesity In Each State")+
  xlab("State")+
  ylab("Obesity Value (%)")+
  theme(axis.text.x=element_text(angle=90,hjust=1))
g

```

